%!TEX root = ../thesis.tex
\chapter{Quad-tree mesh in 2D analysis}
\label{qdt_sec:main}
\section{Introduction}
\paragraph{}
The main objective of this chapter is to implement an adaptor that can parse the geometric information in CAD directly and to develop an automatic mesh generation algorithm based on it.
The IGES file introduced in Sec.~\ref{lr_sec:IGES} is used in the proposed method as the bridge between the CAD and the numerical analysis.
A quad-tree mesh generation algorithm described in \hl{Sec.}~\ref{qt_sc:quadtree} will be adopted to generate a high quality mesh \hl{that meets the scaling requirement discussed in Sec}.~\ref{lr_sec:sbfem}.
Either the NURBS basis function or the traditional shape function can be used as the shape function of the SBFEM solver.
The geometric boundary will be translated into polylines before the meshing and the intersections are calculated based on them.
Intersecting points on these polylines are projected back to the NURBS surface after the meshing is generated to retain the exact geometry.
% We further extend the method to problems with singularities within the framework of linear elastic fracture mechanics.
The proposed method enhances the conventional SBFEM and the salient features of the method are:
    \begin{itemize}
        \item Direct using design file as geometric input\hl{s}
        \item No human effort involvement in mesh generation
        \item Retained exact geometry
        \item High quality mesh generated from the quad-tree algorithm
    \end{itemize}
\paragraph{}
This chapter is organized as follows.
The CAD output (iges file) will be introduced first.
After that, an overview of the algorithm that can generate quadtree mesh will be provided.
Furthermore, a point projection method for NURBS curve utilizing its strong convex hull property is presented.
The accuracy and the convergence properties of the proposed techniques are demonstrated with benchmark problems in the context of linear elasticity, followed by concluding remarks in the last section.


\section{CAD output in 2D}
\label{qt_sc:iges}
\input{quadtree/iges.tex}

\section{Quad-tree structure}
\label{qt_sc:quadtree}
\input{quadtree/quadtree.tex}

\section{Points projection}
\label{qt_sc:projection}
\input{quadtree/projection.tex}


\section{Numerical Examples}
\input{quadtree/ex_cantilever.tex}
\input{quadtree/ex_circular_hole_qdt.tex}
\input{quadtree/ex_bracket.tex}
% \input{quadtree/ex_dam.tex}
\input{quadtree/ex_building.tex}
\input{quadtree/ex_other_mesh.tex}

\section{Conclusions}
\paragraph{}
In this chapter, the IGES file is employed directly from the CAD output to represent the geometry during the preprocessing.
The proposed methods provides a systematic and automatic mesh generation algorithm where \hl{a} high quality mesh \hl{that meets the scaling requirement discussed in Sec.}~\ref{lr_sec:sbfem} is produced efficiently.
The CAD design file can be used directly and the exact geometry can also be retained, which largely reduce the human efforts involved in numerical analysis.
Moreover, it helps to reduce the analytical error as the difference in the geometric representation is minimized.
Computational efficiency is improved via utilizing the pattern of the quadtree to prevent repeated calculation.
Points projection algorithm is accelerated using the strong convex hull property of the NURBS curve.
The accuracy, effectiveness and the convergence properties of the proposed method are demonstrated with benchmark problems in linear elasticity mechanics.
From the numerical studies, it can be observed that the quadtree mesh yield\hl{s} better accuracy compared to uniform mesh with same degree of freedoms.
