%!TEX root = ../thesis.tex
\chapter{Isogeometric enhanced SBFEM in 2D}
\label{Iso_sec:main}
\section{Introduction}
\paragraph{}
The main objective of this chapter is to combine the concept of isogeometric analysis and the SBFEM.
Non-uniform rational B-splines (NURBS) basis functions are employed to approximate the unknown fields in the circumferential direction.
This provides a seamless integration with the CAD model.
The method is further extended to problems with singularities within the framework of linear elastic fracture mechanics and to dynamic analysis.
The proposed method enhances the conventional IGA and the salient features of the method are:
    \begin{itemize}
        \item No tensor-product patches as only the boundary information is required for the stress analysis
        \item Feasible to have a n-sided polygonal domain of mixed type/order of the element on the edges, 
                which leads to high flexibility in meshing and mesh transition
        \item Model strain/stress singularities without enrichment
        \item No internal mesh when studying the dynamic response at high frequencies
    \end{itemize}


This chapter organized as follows.
Section.~\ref{iso_section:formulation} provides an overview of the SBFEM and important equations pertaining to linear elasticity,
followed by extending the formulation to linear elastic fracture mechanics in Section~\ref{iso_section:fracture}.
After that, methods that perform the interpolation of surface traction and displacement will be presented in Section~\ref{iso_section:surface_traction} and Section~\ref{iso_section:interpolation}.
Numerical integration with NURBS will be mentioned in Section~\ref{iso_section:numerical_integration} before the accuracy and the convergence properties of the proposed techniques being demonstrated with benchmark problems in the context of linear elasticity and linear elastic fracture mechanics in Section~\ref{iso_section:examples}, followed by concluding remarks in the last section.
This chapter is published \citep{NATARAJAN2015733}.
%=================================================================================================================================%
\input{isogeometric_sbfem/sbfem_formulation.tex}
\input{isogeometric_sbfem/sbfem_linear_fracture.tex}
\input{isogeometric_sbfem/sbfem_surface_traction.tex}
\input{isogeometric_sbfem/sbfem_displacement_interpolation.tex}
\input{isogeometric_sbfem/nurbs_numerical_integrations.tex}  
%=================================================================================================================================%
\section{Numerical examples}
\label{iso_section:examples}
\paragraph{}
In this section, the accuracy and the convergence properties of the proposed method are demonstrated with a few
    benchmark problems.
First, the proposed method is applied to thick cantilever beam bending, to a plate with a center
    circular hole and to an L-shaped bracket.
In the case of L-shaped bracket both the static and the dynamic responses are studied.
The results are compared with analytical solution where available and with the results obtained using quadratic
    Lagrange shape functions.
In the latter part of the section, problems involving strong discontinuities (e.g., plate with an edge crack,
    angled crack in an orthotropic body) are solved to illustrate the effectiveness of the proposed method.
It is noted that, when the proposed method is applied to problems involving strong discontinuities, no special 
    treatment is required, such as, the augmentation of finite element basis or IGA with asymptotic functions
    \citep{Benson2010} \citep{De2011}.
For the purpose of error estimation and convergence studies, the relative error, L 2 and H 1 norms are used.
The displacement norm is given by:
    \begin{equation}
        \| u - u^h \|_{L^2(\Omega)}=
        \sqrt{
            \int_{\Omega}\left[
                \left(
                    u-u^h
                \right) \cdot
                \left(
                    u-u^h
                \right)
            \right]
        }
    \end{equation}
%
where $u^h$ is the numerical solution and $u$ is the analytical solution or a reference solution.
The energy norm is given by
    \begin{equation}
        \| u - u^h \|_{H^1(\Omega)}=
        \sqrt{
            \int_{\Omega}\left[
                \left(
                    \epsilon - \epsilon^h
                \right)^T D
                \left(
                    \epsilon - \epsilon^h
                \right)
            \right]
        }
    \end{equation}
%
For the purpose of numerical integration of NURBS basis functions, we employ higher order Gaussian quadrature over each span of the NURBS basis functions.
Other quadrature rules are possible as outlined in \citep{Hug2010}.
For Lagrange basis functions, conventional Gauss–Lobatto quadrature is employed.

\input{isogeometric_sbfem/ex_cantilever_beam.tex}

\input{isogeometric_sbfem/ex_circular_hole.tex}

\input{isogeometric_sbfem/ex_l_shaped_bracket.tex}

\input{isogeometric_sbfem/ex_circular_disk_edge_crack.tex}

\input{isogeometric_sbfem/ex_edge_crack.tex}

\input{isogeometric_sbfem/ex_angled_crack.tex}

\input{isogeometric_sbfem/ex_bi_material_plate_with_notch.tex}

%=================================================================================================================================%
\section{Conclusions}
\paragraph{}
In this chapter, the NURBS basis functions are employed to approximate the unknown fields in the circumferential direction within the framework of the SBFEM.
The accuracy, effectiveness and the convergence properties of the proposed method are demonstrated with benchmark problems in linear elasticity and linear elastic fracture mechanics.
From the numerical studies, it can be observed that the NURBS basis functions yield superior accuracy when compared to Lagrange basis functions of the same order.
The proposed method overcomes the disadvantages of both the isogeometric finite element analysis and the isogeometric boundary element method. 
Like in the IGAFEM no fundamental solution is required and like in the IGABEM the spatial dimension is reduced by one.
However, for complicated geometries, to meet the star convexity, subdivision into smaller sub-domains is required.
When applied to problems with singularities, the proposed method does not require additional functions to span the solution space.
Moreover, the proposed framework does not require internal discretization to study the dynamic response at high frequencies.
